---
title: "1.1 Interactive map of survey"
author: "Aranxa Márquez"
output: 
  flexdashboard::flex_dashboard:
    theme: cosmo
    orientation: columns
    vertical_layout: fill
---

Create an interactive leaflet map
 1. Divided by states that are colored in relation to a
 total number of survey responses across all waves
 Following good practice of visualization. 

For this plot, you should:
1. Employ a color palette based on the number range of survey entries.
2. Use the OpenStreetMap.Mapnik provider tile.
3. Create a popup that reads “Total survey responses for {State initials}: {Number}”.
4. Add a color legend with a title.

```{r echo=FALSE}
library(pacman)

p_load(flexdashboard, tidyverse, dplyr, flexdashboard, leaflet, DT, readr, summarytools, ggplot2)

meof_usa_web_df <- readRDS("~/Desktop/Intro to DSc/Hackathon/Hackathon/Clippy_1/tracking/meof_usa_web_df.RDS")

meof_usa_survey_df <- readRDS("~/Desktop/Intro to DSc/Hackathon/Hackathon/Clippy_1/survey/meof_usa_survey_df.RDS")

time_zones <- readRDS("~/Desktop/Intro to DSc/Hackathon/Hackathon/Clippy_1/tracking/time_zones.RDS")
> 


```

Column 
--------------------------------------------------------------------------------------------

### Interactive Table

```{r}

# Preparing the data: new dataframe called new_aribnb |> 1) arrange from highest to lowest price |> 2) select the first and the last 100 rows of the data, |> 3) keep only the columns for "price", "neighbourhood_group" and "room_type" 

new_airbnb <- airbnb_data |> 
  arrange(desc(price)) |> 
  select(price, neighbourhood_group, room_type) |> 
  slice(c(1:100, (n() - 99):n())) |> 
  filter(price != 0) # removed this values because they looked like scam sites

datatable(new_airbnb, options = list(pageLength = 10))
```



Column
--------------------------------------------------------------------------------------------

### Distribution 
```{r}
# b) Univariate distribution chart of one of price, adhering to good practice of plot design.

ggplot(new_airbnb, aes(x = price)) +
  geom_histogram(fill = "skyblue", color = "black", bins = 8) +
  labs(
    title = "Distribution of Airbnb Listing Prices",
    x = "Price",
    y = "Frequency"
  ) +
  scale_x_continuous(limits = c(10, max(new_airbnb$price))) +
  theme_minimal()

```


### Regression
```{r}

# Subset the data
subset_airbnb <- airbnb_data |> 
  arrange(desc(price)) |> 
  select(price, neighbourhood_group, room_type, number_of_reviews, reviews_per_month) |> 
  filter(price != 0)

# Create log_price column in the subset
subset_airbnb$log_price <- log(subset_airbnb$price)

# Fit the linear model using log_price
model_airbnb <- lm(log_price ~ number_of_reviews + neighbourhood_group + reviews_per_month, data = subset_airbnb)

# Treat NA's in reviews_per_month as zeros
subset_airbnb$reviews_per_month[is.na(subset_airbnb$reviews_per_month)] <- 0

# Convert neighbourhood_group to factor and relevel
subset_airbnb$neighbourhood_group <- as.factor(subset_airbnb$neighbourhood_group)
subset_airbnb$neighbourhood_group <- relevel(subset_airbnb$neighbourhood_group, ref = "Manhattan")

# Obtain predicted log-transformed prices
predicted_airbnb <- predict(model_airbnb, newdata = subset_airbnb)

# Create a comparison plot
plot(subset_airbnb$log_price, predicted_airbnb,
     xlab = "Actual log(price)",
     ylab = "Predicted log(price)",
     main = "Actual vs Predicted log(price)")

# Obtain actual prices from the subset
actual_prices <- subset_airbnb$price

# Convert predicted log prices back to original prices
predicted_prices <- exp(predicted_airbnb)

# Create a comparison plot
plot(actual_prices, predicted_prices,
     xlab = "Actual Price",
     ylab = "Predicted Price",
     main = "Actual vs Predicted Price")
abline(0, 1, col = "red")  # Adds a diagonal line for reference

```


Column 
--------------------------------------------------------------------------------------------

### 100 Airbnb Host Location Random Sample 
```{r}
# d) Create an interactive `leaflet` map, mapping a random subsample of 100 of the host locations.

# Sample data generation
set.seed(42)
airbnb_sample <- airbnb_data[sample(nrow(airbnb_data), 100), ]

leaflet(airbnb_sample) |> 
  addTiles() |> 
  addMarkers(~longitude, ~latitude, popup = ~paste("Latitude:", latitude, "<br>Longitude:", longitude))

```

